Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2013-12-13 ms.tex
more text

\subsection{Molecular Emission}

\subsection{Point Sources}

@@

At each sky location, we have five independent intensity 
measurements (four ) FDS99 found typical values for T2 and

@@

\section{Pixelization}
For the purpose of fitting, we break the sky into independent pixels of 
angular diameter $\sim$, defined by the HEALPix pixelization with nside=2048. 
This is convenient because the Planck maps are provided in this format and 
this pixelization adequately samples the $6.1'$ resolution maps under 
consideration. We reiterate that each pixel is fit independently of 
neighboring pixels.

@@

\begin{equation}
P(I^{*}_{545}, T_2) \propto L({I_i}|I^{*}_{545}, T_2)P(T_2)
\end{equation}

@@

@@

Based on observations obtained with Planck (http://www.esa.int/Planck), 
an ESA science mission with instruments and contributions directly funded 
by ESA Member States, NASA, and Canada.

>>>>

\subsection{Molecular Emission}
One advantage of the FIRAS data used by FDS99 was its many narrow bins in 
frequency, which allowed those frequency ranges contaminated by strong 
molecular line emission to be discarded from the analysis. Unfortunately, with 
the broad \PLANCK~and \IRAS~bandpasses we do not have such a luxury. This means
 that we cannot truly separate out the thermal continuum of dust emission we 
wish to study from the molecular line emission. The most prominent molecular 
line emission in the Planck bands of interest arises from CO lines in the XX, 
YY bands. We investigated the possibility of subtracting out CO emission based 
on the template of

\subsection{Compact Sources}
To mask compact sources, we use the SFD compact source mask, which was 
originally constructed to mask point sources and resolved compact objects
that are not part of the Galactic cirrus at 3000 GHz. Given our pixelization 
(see $\S$\ref{sec:pix}), 1.56\% of pixels are masked. We have inspected all of 
the maps used in this analysis and do not see any evidence that this compact 
source mask fails to adequately mask compact sources in the \PLANCK~data. In 
practice, we perform our dust SED fits in all pixels, even those flagged by 
the point source mask. Compact source affected pixels can be ignored or 
interpolated over downstream.
%maybe say that we're releasing a version of the map with point sources
%interpolated over by us as well

@@

At each sky location, we have five independent intensity 
measurements (four ) FDS99 found typical values for $T_2$ and

@@

\section{Pixelization}
\label{sec:pix}
For the purpose of fitting, we break the sky into independent pixels of 
angular size $\sim$1.72$'$, defined by the HEALPix pixelization with nside=2048 \citep{healpix}. 
This is convenient because the Planck maps are provided in this format and 
this pixelization adequately samples the $6.1'$ resolution maps under 
consideration. We reiterate that each pixel is fit independently of 
neighboring pixels.

@@

\begin{equation}
P(I^{*}_{545}, T_2) \propto \mathcal{L}(\{I_i\}|I^{*}_{545}, T_2)P(T_2)
\end{equation}

@@

%mention something about the proposal distribution at some point?

@@

This material is based upon work supported by the National Science Foundation 
Graduate Research Fellowship under Grant No.Based on observations obtained with
 Planck (http://www.esa.int/Planck), an ESA science mission with instruments 
and contributions directly funded by ESA Member States, NASA, and Canada. This 
research made use of the NASA Astrophysics Data System (ADS) and the IDL 
Astronomy User's Library at Goddard. \footnote{Available at 
\texttt{http://idlastro.gsfc.nasa.gov}}
